Appendix

### 2022-07-21 writing/appendix_sep.Rmd
update latest version of manuscript and appendix

---
title: Appendix 
output:
  pdf_document: default
---

```{r}
library(tidyverse)
```

Tracing Scores

>>>>

---
title: Appendix 
author: 
  - name          : "Blinded"
documentclass     : "docx"
classoption       : "man"
output            : papaja::apa6_doc
bibliography      : ["references.bib"]

---

```{r}
knitr::opts_chunk$set(fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=FALSE, message = FALSE, sanitize = TRUE)
```

```{r}
library(papaja)
library(tidyverse)
```

# Tracing Scores
